A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add sifting algorithm description

>>>>

The sifting algorithm therefore uses a brute-force enumeration strategy. It starts
by swapping the processed variable $x$ downwards one level at a time, i.e. swapping 
it with its successor variable, which is located on the layer below in the OBDD.
This is done until $x$ is the next to last variable in the OBDD. Then, this is
done in the other way round, i.e. swapping $x$ with its predecessor variable until
$x$ becomes the top variable of the OBDD. While proceeding, the ideal position
is memorized and after $x$ became the top variable, $x$ is moved to this ideal
position by, again, swapping levels one by one.
